\documentclass[a4paper,11pt]{jsarticle}

% 数式
\usepackage{amsmath,amsfonts}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{amssymb}

% 表
\usepackage[utf8]{inputenc}
\usepackage{diagbox} % 斜線付きセルを作成するために必要
\usepackage{booktabs} % 表の罫線を美しくするために必要
\usepackage{hhline} % 水平罫線を制御するために必要

% 画像
\usepackage[dvipdfmx]{graphicx}
\usepackage{ascmac}
\usepackage{physics}
\usepackage{float} % 追加

% 図
\usepackage[dvipdfmx]{graphicx}
\usepackage{tikz} %図を描く
\usetikzlibrary{positioning, intersections, calc, arrows.meta,math} %tikzのlibrary

% ハイパーリンク
\usepackage[dvipdfm,
  colorlinks=false,
  bookmarks=true,
  bookmarksnumbered=false,
  pdfborder={0 0 0},
  bookmarkstype=toc]{hyperref}


% カラー
\usepackage{color}

% 式番号を章ごとにリセット
\numberwithin{equation}{section}

\begin{document}

\title{English diary}
\author{Yuri OGAMI}
\date{\today}
\maketitle

\subsection*{12/26}
\subsubsection*{original}
Today, I started to write this diary to improve my English skill.\\
In the morning, I got exercised. I was so exhausted that I can't study after that.\\
After exercising, I sent my books to the customer. It was my first time to do that.\\
In the evening, I started to study physics, especially thermodynamics. However it was too difficult for me to fully understand it.
So, I quit studying it right away.

\subsubsection*{revised}
Today, I started \textcolor{red}{writing} this diary to improve my English \textcolor{red}{skills}.\\
In the morning, I \textcolor{red}{exercised}. I was so exhausted that I \textcolor{red}{couldn’t} study \textcolor{red}{afterward}.\\
After exercising, I sent \textcolor{red}{some} books to \textcolor{red}{a} customer. It was my first time \textcolor{red}{doing} that.\\
In the evening, I started \textcolor{red}{studying} physics, especially thermodynamics. However, it was too difficult for me to fully understand, \textcolor{red}{so I stopped studying it} right away.

\subsubsection*{others}
The road was so \textcolor{red}{slippery} that I almost fell down. The \textcolor{red}{icy} surface made the road dangerously \textcolor{red}{slippery}.\\
If I don't want don't study physics tomorrow, I will make many gyoza.\\
If I \textcolor{red}{don't feel like} studying physics tomorrow, I'll \textcolor{red}{make lots of} gyoza.

\end{document}